% 3456789012345678901234567890123456789012345678901234567890123456789012
%        1         2         3         4         5         6         7
%
% Format: LaTeX
%
% For information about this file, contact the author by email at
% mailto:rjl@applied-math.org or telephone: +1 303 221 4380.  The
% time zone is GMT minus seven hours.  Mobile when I am in the UK
% is +44 (0)7984 147 430.
%
% It is presently formatted for 8-1/2x11 inch US-letter paper.
%

\documentclass[letterpaper]{article}

% The geometry package lets me control the page margins.
\usepackage[margin=1in]{geometry}

% The cmap package avoids the problem of ligatures like 'ffi' disappearing from a
% copy and paste operation where the destination is plain text.  This is important
% when sending out résumés in PDF if you want keywords to be spotted by automated
% filters used by HR.  Without the `resetfonts' option it doesn't do the trick with
% Computer Modern Roman.
\usepackage[resetfonts]{cmap}

% The titling package lets me control white space at the top of the first page.
\usepackage{titling}
\setlength{\droptitle}{-0.95in}

% Used for graphics
\usepackage{graphicx}

% The hyperref package makes links show up in generated PDF files.
\usepackage{hyperref}
\usepackage{url}

% The xcolor package is used to grey out text in the Social Networking section at the end.
\usepackage{xcolor}

\textheight=9in
\raggedbottom
\raggedright
\def\nodate{\@makedatefalse}
\date{}

\title{\textsc{Joe Loughry}\vspace{-5mm}}
\author{\hspace{-4mm}\vspace{-5mm}\emph{Cross Domain System Certification and Accreditation (C\&A),
	Computer Security Research}
}

\newcommand{\redacted}{\textsc{[title redacted]}}

\begin{document}
\maketitle

\vspace{-10mm}\hspace{-3mm}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	6214 South Krameria Street        & St Cross College \\
	Centennial, CO 80111-4243         & St Giles \\
	USA                               & Oxford, Oxon\ OX1 3LZ\ UK \\
	\url{mailto:rjl@applied-math.org} & \url{mailto:joe.loughry@stx.ox.ac.uk} \\
	Home: (303) 221-4380              & Mobile: +44 (0)7984 147 430 \\
\end{tabular*}

\section*{Keywords for Regexes} % FINE TUNE THIS SECTION!

Certification and Accreditation (C\&A) of cross domain systems,
Assessment and Authorization (A\&A) in classified environments,
Certification Test \& Evaluation (CT\&E),
Security Test and Evaluation (ST\&E),
penetration testing,
DIACAP,
Common Criteria,
DCID 6/3,
Compartmented Mode Workstation (CMW) programming,
UNIX,
Trusted Solaris v2.5--8,
software development,
R\&D,
principal investigator,
technical writing,
U.S.\ citizen,
TS/SCI clearance,
DoD 8570.01 certified CISSP-ISSEP,
lived overseas,
programming,
publications,
patents,
public speaking,
funding,
and teaching experience.

\section*{Work Experience} % most recent first

\begin{itemize}
	\item Graduate Research Student, University of Oxford, Oxon, England, from 2012--present.

		\begin{quote}\vspace{-2mm}
			\emph{Having wrapped up a three-year R\&D contract for the Air Force Research
			Lab in January of 2012, it was necessary to finish writing my dissertation by
			the deadline.}
		\end{quote}

	\item Information Assurance Engineer, Lockheed Martin Corporation, from 2006--2012.

		\begin{quote}\vspace{-2mm}
			\emph{Reorganised into the INFOSEC group at Lockheed, I designed a new
			cryptosystem leading to another patent application and began studying
			government security evaluation standards.  Deciding to solve the C\&A problem once
			and for all, I took my thesis to the CS department, telecommuting from the UK and
			proposing and winning an AFRL contract while I was gone.}
		\end{quote}

	\item Software Engineer, Lockheed Martin IS\&GS Western Region, from 1998--2006.

		\begin{quote}\vspace{-2mm}
			\emph{The optical TEMPEST research, not yet published in the open literature but of
			considerable interest to the intelligence community, led to a security clearance and
			a job writing code for Trusted Solaris.  I travelled around the U.S.\ and Britain
			writing code and installing systems and got interested along the way in
			Certification and Accreditation (C\&A) of systems.}
		\end{quote}

	\item System Administrator, Wells Fargo \& Company, Seattle, Washington, from  1996--1997.

		\begin{quote}\vspace{-2mm}
			\emph{After being acquired by Wells Fargo, I moved to sysadminning its network
			of X terminals, Cisco routers, and structured cabling.  Using the facilities
			at Seattle U., I ran experiments in optical TEMPEST that would eventually
			be cited in 14 books on information security.}
		\end{quote}

	\item Programmer/Analyst II, First Interstate Bank of Washington, Seattle, from 1990--1996.

		\begin{quote}\vspace{-2mm}
			\emph{Five people at the bank wrote software, mostly in machine language, for a few
			hundred PCs in 150 bank branches around the state.  Network communications were
			limited to one-way, piggybacked on IBM 3270 terminal traffic with some local
			storage in the 4702 controllers.  With no way to back out changes from production,
			we were extremely careful how we did it.}
		\end{quote}

\end{itemize}

\section*{Education} % most recent first

\begin{itemize}
    \item Oxford University, Department of Computer Science,
		doctoral student.  Dissertation title: \emph{Security Test and Evaluation
		of Cross Domain Systems} (degree expected at the end of 2012).

    \item Master of Software Engineering (M.S.E.), Seattle
		University / Seattle, Washington (1996).

    \item Bachelor of Arts in Mathematics, University of
		Colorado / Boulder, Colorado (1986).
\end{itemize}

\section*{Security Clearance}

\begin{itemize}
	\item TS/SCI is current; last investigation date: 5th August 2009 (SSBI PR);
		last CI poly 26th May 2010.
\end{itemize}

\section*{Refereed Journal Publications} % most recent first

\begin{itemize}
    \item `Information Leakage from Optical Emanations' by J.\ Loughry
    and D.A.\ Umphress. \emph{ACM Trans.\ Info.\ Sys.\ Security} \textbf{5}(3).
    pp.\ 262--289, 2002.
\end{itemize}

\section*{Conference Publications} % most recent first

\begin{itemize}
	\item `Information Asymmetry in Classified Cross Domain System Accreditation'.
		\emph{C\&ESAR 2012}, Rennes, France, 20--22 November 2012.  To appear.

	\item `Unsteady Ground: Certification to Unstable Criteria'.
		\emph{Second International Conference on Advances in System Testing
		and Validation Life Cycle}. Nice, France, 2010. 

	\item `Evaluation of Existing IT Systems Under the Common Criteria
		at Levels Above EAL4'. \emph{Oxford University
		Computing Laboratory Student Conference}, Oxford, U.K., 2008.

    \item `Use of XML in the Specification and Development of a New High
		Assurance Controlled Interface'. \emph{Network Centric Warfare} conference,
		Washington, D.C., 2003.

    \item `Optical Remote Interception of Networks (\textsc{Orion})'
		\emph{InfowarCon '02}, Washington, D.C., 2002.

    \item `\textsc{Radiant Mercury}'. \emph{Cross Domain Solutions
		Organization}. Johns Hopkins University Applied Physics Laboratory,
		Laurel, Maryland USA, 2001.

    \item `Performance evaluation for line-drawing recognition systems'
		by Ihsin T. Phillips, Frank Chang, Kevin Chang, Bhavani Duggirala,
		Mike Logan, Joe Loughry, and Jisheng Liang. \emph{Proc.\ SPIE '97
		Document Imaging IV}. Vol.\ 3027, pp.\ 136--148, March 1997.
\end{itemize}

\section*{Other Published Reports} % most recent first

\begin{itemize}
	\item `Probabilistic Redaction' final technical report. Air Force Research
		Laboratory (AFRL), Rome, New York, 2012.  Available from the Defense Technical
		Information Centre (DTIC), Washington, D.C.

	\item `Subsets of an 8-element set in order by number of elements in each
		subset'. \emph{On-line Encyclopedia of Integer Sequences}, AT\&T Research, 2003.

	\item `Efficiently enumerating the subsets of a set' by J. Loughry, J. von Hemert,
		and L. Schoofs (1998).  In preparation.

    \item Sun Microsystems security advisory (software): \redacted\ classified S//NF, 1999.
	\item Sun Microsystems security advisory (hardware): \redacted\ classified S//NF, 1998.
	\item Sun Microsystems security advisory (software): \redacted\ classified S//NF, 1998.
	\item Sun Microsystems security advisory (software): \redacted\ classified SI TK B, 1998.

    \item RISKS \emph{(ACM Forum on Risks to the Public in Computers
    and Related Systems)} vols 17.31, 21.94--5, 22.81, 24.07,
    24.22--3, 24.55, 24.87, 25.73, and 26.46.
\end{itemize}

\section*{DoD 8570.01 Certifications}

\begin{itemize}
	\item CISSP-ISSEP certificate no.\ 10411, current and satisfies IAT Level III,
		IAM Level III, and IASAE III.
\end{itemize}

\section*{Patents} % most recent first

\begin{itemize}
	\item Application 13/355,210 \emph{Nested Digital Signatures with Constant File Size},
		filed 20th January 2012.

    \item US 6,987,461 \emph{System and Method for Addressing Optical
		Emanations from an Information Processing Device}, issued 17th January 2006.
\end{itemize}

\section*{Funding}

\begin{itemize}
	\item Awarded \$968,412.00 for `Probabilistic Redaction', USAF Rome Lab contract
	no.\ FA8750-09-C-0006, Principal investigator (PI) for period of performance
	2009--2012, project completed.
\end{itemize}

% \item `Nested Digital Signatures'. Disclosure ID MG-03529 (2011).
%
% \item (with Greg Edwards) `Selective denial of wifi in an area'.
%	Disclosure ID WD-00467 (2008).
%
% \item `Probabilistic Redaction'. Disclosure ID WD-00466 (2008).
%
% \item Lockheed Martin Aeronautics, Ft.\ Worth, TX. `Certification
%	and Accreditation Processes in Joint Strike Fighter (JSF)
%	International Partner Countries' (2006).
%
% \item Lockheed Martin Systems Integration, Owego, NY. `Data
%	Remanance and Declassification Issues in the Netra 240 Server'.
%	Document SSYR-TRD-10859 (2006).
%
% \item United States Navy, Space and Naval Warfare Systems Centre,
%	San Diego. `Risk Assessment for Internetwork Connection'. Document
%	SSYR-TRD-10860 (2006).
%
% \item Lockheed Martin Corporation. \emph{RTG 1.0 Descriptive
%	Low-Level Design (Informational Annex)}. Document
%	SSYR-050-10424-001:47 (2006).
%
% \item United States Navy. \emph{\textsc{Radiant Mercury} IAVA
%	Process}. Document USN-PRO-10640-001 (2006).
%
% \item Lockheed Martin Corporation, Integrated Systems and
%	Solutions. \emph{Radiant Trust Gold 1.0 Security Target}.  Document
%	SSYR-050-10424-000:66 (2006).
%
% \item `Method for Applying Digital Signature to Streaming Video
%	from a Trusted Source'. Trade Secret Disclosure ID DA-01193 (2005).
%
% \item National Security Agency. \emph{Draft U.S. Government
%	Protection Profile for Automated Guard and Sanitizer For High
%	Robustness Environments} (2004).
%
% \item Lockheed Martin IS\&S. `High Assurance Layer-1
%	Cross-Correlation Guard'. U.S. Patent Filing VF-03302 (2004).
%
% \item `Cross-Domain Voice-over-IP (VoIP) Guard'. Disclosure ID DA-01112 (2003).
%
% \item `Smart Card with On-Board Guard'. Disclosure ID DA-01113 (2003).
%
% \item `Visual Identification System for Cables'. Disclosure ID DA-01085 (2003).
%
% \item United States Air Force---Air Combat Command. \emph{B-2
%	Centre Instrument Display Subsystem Block II Upgrade Security
%	Guard Board Jumpstart Process} (2001).
%
% \item Lockheed Martin Space Systems. `Radiant Mercury Imagery
%	Guard Cryptographic Architecture' (1998).

\section*{Teaching Experience} % most recent first

\begin{itemize}
    \item University Instructor, CSCE 591 \emph{Computer Networks},
    Seattle University, Spring Quarter 1998.
\end{itemize}

\section*{Officerships and Committee Work}
\begin{itemize}
	\item April, 2012: Co-organiser of a public debate on the subject of ageing between
		Dr Aubrey de Grey and Prof.\ Colin Blakemore, chaired by Professor Sir Richard Peto,
		attended by 650 people in the Sheldonian Theatre, Oxford.
	\item 2009--present: President of the Oxford Lyceum.
	\item 2009--present: IT Officer, Oxford University Scientific Society.
	\item Chair of the OXFORD-CS-2011 Conference Programme Committee.
	\item Member of the COMLAB-CS-2010 Conference Programme Committee.
	\item Member of the COMLAB-CS-2009 Conference Programme Committee.
	\item 2007--09: Treasurer of the Oxford Lyceum.
	\item Science fair judge for the Ricks Centre at the University of Denver (2012).
\end{itemize}

\definecolor{grey}{rgb}{0.55,0.55,0.55}

\section*{Social Networking {\small (lesser used social networks are \textcolor{grey}{greyed out})}}

% The following progression colours look good on screen but the latter ones print too faintly:
% \definecolor{grey}{rgb}{0.5,0.5,0.5}
% \definecolor{lightgrey}{rgb}{0.75,0.75,0.75}
% \definecolor{verylightgrey}{rgb}{0.875,0.875,0.875}

% The following colours print well but are too similar on screen:
% \definecolor{grey}{rgb}{0.3,0.3,0.3}
% \definecolor{lightgrey}{rgb}{0.4,0.4,0.4}
% \definecolor{verylightgrey}{rgb}{0.5,0.5,0.5}

\begin{itemize}
	\item Google Scholar: \url{http://scholar.google.com/citations?hl=en&user=PX_U29EAAAAJ}
	\item GitHub: \url{https://github.com/jloughry}
	\item LinkedIn: \url{http://www.linkedin.com/in/jloughry}
	{\color{grey}
		\item Twitter: \url{https://twitter.com/jloughry}
		\item Google+: \url{https://plus.google.com/u/0/115779672587479359864/}
		\item Facebook: \url{https://www.facebook.com/joe.loughry.oxford}
	}
\end{itemize}

\section*{Code contributed to the following Open Source projects}

\begin{itemize}
	\item OpenSolaris: \url{http://www.opensolaris.org} (2006) \emph{bug in password
		retry limit of TSOL 8}
	\item The FreeBSD Project: \url{http://www.freebsd.org} (1999) \emph{contributed new
		console screensaver}
	\item Fetchmail: \url{http://fetchmail.berlios.de} (1998) \emph{patch to handle multihomed
		machines}
\end{itemize}

\vfill
{\tiny Build \input{build_counter.txt}}

\end{document}
