% 3456789012345678901234567890123456789012345678901234567890123456789012
%        1         2         3         4         5         6         7
%
% Format: LaTeX
%
% For information about this file, contact the author by email at
% mailto:rjl@applied-math.org or telephone: +1 303 221 4380.  The
% time zone is GMT minus seven hours.  Mobile when I am in the UK
% is +44 (0)7984 147 430.
%
% It is presently formatted for 8-1/2x11 inch US-letter paper.
%

\documentclass[12pt,letterpaper]{article}

% The cmap package avoids the problem of ligatures like 'ffi' disappearing from a
% copy and paste operation where the destination is plain text.  This is important
% when sending out résumés in PDF if you want keywords to be spotted by automated
% filters used by HR.  Without the `resetfonts' option it doesn't do the trick with
% Computer Modern Roman.
%
% I use a modified ot1.cmap and a modified oms.cmap and a modified cmap.sty file
% in the current directory to tell PDF that in addition to the ligatures mentioned
% above it should also replace curly quotes with straight quotes, en dashes and em
% dashes with hyphens, and bullets with asterisks or other ASCII characters.  Copy
% and paste of text from the resulting PDF file will be 7-bit clean ASCII containing
% no Unicode characters at all.  Be sure to load cmap immediately after the
% documentclass line so it can see all the fonts as they are loaded.  This version
% of cmap.sty works with 11pt and 12pt options to documentclass unlike the original.
\usepackage[resetfonts]{cmap}

% The geometry package lets me control the page margins.
\usepackage[margin=1in]{geometry}

% The titling package lets me control white space at the top of the first page.
\usepackage{titling}
\setlength{\droptitle}{-25mm}

% The url package formats URLs nicely.
\usepackage{url}

% The hyperref package makes links show up in PDF files and must be loaded last.
\usepackage{hyperref}

\raggedbottom

\def\nodate{\@makedatefalse}
\date{}

\title{\textsc{Joe Loughry}\vspace{-7mm}}

\author{\emph{Cross Domain System (CDS) Software Development and C\&A}}

\begin{document}
\maketitle
\thispagestyle{empty}

\vspace*{-20mm}
\section*{One Page Resume}

\begin{itemize}
	\item At the present time, I am writing a doctoral dissertation on \emph{Security Test and
		Evaluation of Cross Domain Systems} at the University of Oxford.
	\item 1998--2012 at Lockheed Martin Corporation:
		\begin{itemize}
			\item \textbf{Information Assurance Engineer} for the last six years; before that,
				eight years as a \textbf{software engineer on Radiant Mercury}.
				\begin{itemize}
					\item Invented constant-space digital signatures (a patent application
						13/355,210 has been filed but not yet published) used for
						imagery analysis.
					\item Proposed and won
						\href{http://applied-math.org/Probabilistic_Redaction.pdf}{\$968,412.00
						contract} from Air Force Research Laboratory for a `probabilistic
						redaction' system while telecommuting from grad school.
					\item \href{http://applied-math.org/acm_optical_tempest.pdf}{Discoverer}
						of the optical TEMPEST effect;
						\href{http://www.google.com/patents/US6987461}{patent no.\ 6,987,461}
						assigned to Lockheed Martin.
					\item C and UNIX programmer with Trusted Solaris, DCID 6/3, cross domain,
						and DIACAP experience.
				\end{itemize}
		\end{itemize}

	\item 1990--97 at Wells Fargo \& Company:
		\begin{itemize}
			\item I worked as a programmer and sysadmin for the bank.
				\begin{itemize}
					\item Faced with a poorly documented mainframe application written in
						\href{https://github.com/jloughry/BANCStar/blob/master/README.md#code-sample}{machine language},
						I solved that problem once and for all by writing a compiler for it.
					\item After working for a few years, I enrolled part time for a master's
						degree in software engineering at Seattle University (M.S.E., 1996).
				\end{itemize}
		\end{itemize}

	\item Prior to 1990, I was still in school:
		\begin{itemize}
			\item B.A.\ in math from the University of Colorado at Boulder.
		\end{itemize}

	\item I have a security clearance and have had all my DoD 8570.01 shots already.
		I can satisfy your requirement for IAT Level III, IAM Level III, or IASAE Level III.
		
\end{itemize}

\section*{Contact Information}

\begin{itemize}
	\item 6214 S.\ Krameria St. \\
		Centennial, CO 80111-4243 \\
		USA

	\item Telephone: (303) 221-4380

	\item Email: \url{mailto:rjl@applied-math.org}
\end{itemize}

\vfill\noindent{\tiny \LaTeX\ build \input{build_counter.txt}}

\end{document}
