\vspace{-2mm}
\section*{Peer-Reviewed Conference Presentations}
\vspace{-3mm}

\begin{itemize}
  \item ``Basilisk'' (arXiv preprint) 1 September 2022.\vspace{-2.5mm}

  \item ``Measurements Toward a Theory of Light Emitting Diode Reversal Attacks,
  Part 1: Error Avoidance''. \emph{EMC Europe 2020}, Rome, Italy (virtual),
  23--25 September 2020.\vspace{-2.5mm}

  \item `(``Oops! Had the silly thing in reverse'')---Optical Injection
  Attacks in through LED status indicators'.
  \emph{EMC Europe 2019}, Barcelona, Spain, 2--6 September 2019.\vspace{-2.5mm}

  \item ``Optical TEMPEST.'' \emph{Int.\ Sym.\ Electromagnetic Compatibility},
    Amsterdam, 27--30 Aug.\ 2018.\vspace{-2.5mm}

	\item ``\href{http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=6699004}%
{A Model of Certifier and Accreditor Risk Calculation for Multi-Level
Systems}.'' \emph{Proc.\ 13th IEEE Int.\ Conf.\ Tech.\ Homel.\ Sec.\ (HST'13)}.
Boston, Massachusetts, 12--14 November, 2013.\vspace{-2.5mm}

	\item
``\href{http://cnadocs.com/papers/CESAR2012_information_asymmetry.pdf}%
{Information Asymmetry in Classified Cross Domain System Accreditation}.''
\emph{19th Comp.\ \& Elec.\ Sec.\ Appl.\ Rend.\ (C\&ESAR 2012)}. Rennes,
France, 20--22 Nov.\ 2012, pp.\ 19--28, 2012.\vspace{-2.5mm}

	\item
``\href{http://ieeexplore.ieee.org/xpl/articleDetails.jsp?arnumber=5617171}%
{Unsteady Ground: Certification to Unstable Criteria}.'' \emph{Second
International Conference on Advances in System Testing and Validation Life
Cycle}. Nice, France, 2010. \vspace{2.5mm}

	% \item ``\href{http://www.cs.ox.ac.uk/files/1328/RR-08-10.pdf}{Evaluation of
	%	Existing IT Systems Under the Common Criteria at Levels Above EAL4}.''
	%	\emph{Oxford University Computing Laboratory Student Conference}. Oxford,
	%	U.K., 2008.

% 	\item ``\href{http://cnadocs.com/papers/xml_paper.pdf}%
% {Use of XML in the Specification and Development of a New High Assurance
% Controlled Interface}.'' \emph{Proc.\ 2nd Network Centric Warfare Conf.},
% Washington, D.C., 22nd Jan.\ 2003.

\end{itemize}

